\documentclass{article}
\usepackage[letterpaper, margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{minted}
\usepackage{notebook}
\usepackage{setspace} % To control linespacing
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{enumerate} % For enumerating lists
\usepackage{enumitem} % more enumerating stuff
\usepackage{multicol} % for multicoumn formating
\usepackage{multirow} % for multicoumn formating
\usepackage{adjustbox}
\usepackage{arydshln}
\usepackage{changepage}
\documentclass{standalone}

\usepackage{csvsimple}
\usepackage{fancyhdr}
\usepackage[usenames,dvipsnames]{xcolor} %To change text colors, color options located at: http://en.wikibooks.org/wiki/LaTeX/Colors
\usepackage[font={footnotesize}]{caption}
\usepackage[labelfont=bf]{caption}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{titlesec} % To control section colors
\usepackage{color}
\usepackage{hyperref} % for web links
\usepackage[toc, acronym, nopostdot, style=long]{glossaries}
    \makeglossaries
    
\title{PowerLab Notebook}
\author{Midrar Adham}
\date{last updated: \today}

\begin{document}

    \maketitle
    \newpage
    
    \tableofcontents
    \newpage
    
    \input{glossaries.tex}
    \printacronyms[type=\acronymtype, nonumberlist]
    % \newpage
    % \label{List of Errors}
    % \input{List of Errors.tex}

    \newpage
    % \input{Fall2020/errors}
    \listoferrors
    \begin{enumerate}
        \item convergence iteration limit reached for object node:34
    \begin{itemize}
        \item  This error mostly refers to transformers ratio (downstream). Make sure the the primary and secondary voltages satisfy the transformer configuration object.
    \end{itemize}
        \item Unable to load player file.
        \begin{itemize}
            \item Make sure player file in the same directory as the glm file.
        \end{itemize}
        \item unable to set current process affinity mask, err code 5
        \begin{itemize}
            \item This is a common error for GridLAB-D version < 3.2. Write gridlabd --version in command window. If it shows any version that is less than 3.8, update your version from \url{sourceforge.com} or use GitHub source code.
        \end{itemize}
        \item expected ';' at end of property specification
        \begin{itemize}
            \item This is a general error. If your file has ";" at the end of each property, then this refers to spaces between numerical values. For example, assuming you defined a voltage value for a transformer object as "120 + 0j;", GridLAB-D will produce the above error. The above value should be written as "120+0j;" without any spaces.
        \end{itemize}
        \item : sync$\_$player:11: not enough values on line
        \begin{itemize}
            \item Each property in player object must be indented. If you add a property in any object, make sure you press "tab" on your keyboard instead of adding spaces.
        \end{itemize}
        \item sync$\_$node(obj=6;mds$\_$primary$\_$node$\_$SwingNode): All nodes were not properly populated
        \begin{itemize}
            \item First of all, make sure you add a "name" property to any object in your glm file. Thus, if there is an error in your file, GridLAB-D will tell you the name of the object that is causing the error. Second, to resolve the above error, make sure the indicated node is linked to another object using a link-based object (line object, link object, triplex line object, ..). Nodes in glm file SHALL not be left hanging.
        \end{itemize}
        \item ERROR [INIT] : init$\_$transformer(obj=4;tranformer1): transformer:4 (split phase) - tranformer1 has a phase mismatch at one or both ends
        \begin{itemize}
            \item SINGLE$\_$PHASE$\_$CENTER$\_$TAPPED transformers connects two nodes. The primary node SHALL be a 3$\phi$ node and the secondary node SHALL be a 1$\phi$ node. Also, in "phases" property, make sure you add the phase name and the letter "S". For example, for a phase A triplex transformer, "phases" property SHALL be defined as "phases AS;".
        \end{itemize}
    \end{enumerate}
    \addcontentsline{toc}{section}{List of Errors}
    \newpage
    \listofwarnings
    \begin{enumerate}
        \item switch object may not behave properly under FBS!
        \begin{itemize}
            \item This warning is a bit misleading and might cause serious issues in the future. FBS is mostly used with strictly radial topologies. Beside the fact that your system "should" be radial or meshed, this also means that your link-based objects should use "from" and "to" properties to connect objects with each other. If you're using NR solver instead of FBS, "from" and "to" properties can be neglected. Instead, you can simply use "line" objects to connect nodes with each other.
        \end{itemize}
    \end{enumerate}
    \addcontentsline{toc}{section}{List of Warnings}
    \newpage
    
    % NEW ENTRIES
    %=========================================================================
    
    \input{Fall2020/all-sprints}
    \input{Winter2021/all-sprints-winter21}
    % \input{Fall2020/errors}
    %=========================================================================
    \newpage
    \nocite{*}
    \bibliographystyle{IEEEannot}
    \bibliography{bibfile}

\end{document}
